Co-citations in context

### 2019-09-12 cocit_r_v2.tex
small fixes to response to review

\begin{itemize}
\item An illustration has been provided
\item Yes, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around. The local model accounts for this but the global one does not
\item The relationship between novelty and conventionality is not a ground truth, we have never claimed it is. This framework was developed by Uzzi et al. (2013) and we have used it to enable \emph{ceteris paribus} comparisons
\end{itemize}

\subsection{Editor}
\emph{I have one other suggestion. In addition to the work on novelty by Brian Uzzi and colleagues, there is also work on novelty by Reinhilde Veugelers and colleagues, who operationalize novelty in a different way. For completeness, you may consider providing a brief discussion of the work by Veugelers and colleagues in your manuscript.}
\begin{itemize}
\item We thank you for bringing this to our attention. Discussing this paper broadens the scope of our manuscript and we've referenced it in the Discussion. As one of our co-authors pointed out, the definition of novelty is a little restrictive to say the least but the rest of the paper is excellent.
\end{itemize}

@@

\textcolor{blue}{A related study by \cite{wang_bias_2017} also uses journal pairings to study novelty in scientific publications but focuses on previously undetected journal pairs to generate a novelty index}

@@

\textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one. Such grouping, while appealing on account of relative simplicity, obscures measurements of novel pairings at the article level. Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\cite{traag_louvain_2019, klavans_which_2017}}. Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.

>>>>

\begin{itemize}
\item An illustration has been generated that will become part of supplementary material.
\item Yes, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around. The local model accounts for this but the global one does not. We argue consistently that local models reduce mis-specification.
\item The relationship between novelty/conventionality and citation impact is not a ground truth, we have never claimed it is. This framework was developed by Uzzi et al. (2013) and we have used it to enable \emph{ceteris paribus} comparisons. We cannot address the question of the huge unstated assumption- we don't think we make such an assumption.
\end{itemize}

\subsection{Editor}
\emph{I have one other suggestion. In addition to the work on novelty by Brian Uzzi and colleagues, there is also work on novelty by Reinhilde Veugelers and colleagues, who operationalize novelty in a different way. For completeness, you may consider providing a brief discussion of the work by Veugelers and colleagues in your manuscript.}
\begin{itemize}
\item We thank you for bringing this to our attention. We really ought to have cited it but we perhaps myopically focused on the details of the random graph approach. Discussing this paper broadens the scope of our manuscript and we've referenced it in the Discussion. As one of our co-authors pointed out, the definition of novelty is a little restrictive to say the least but the paper is an excellent one. \end{itemize}

@@

\textcolor{blue}{A related study by \cite{wang_bias_2017} also uses journal pairings to study novelty in scientific publications, but focuses on previously undetected journal pairs to generate a novelty index. }

@@

\textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one. While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores. Such grouping, while appealing on account of relative simplicity, obscures measurements of novel pairings at the article level. Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\cite{traag_louvain_2019, klavans_which_2017}}.  Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
